---
title: "STA 523 Final Project Write Up"
author: "Jie Sun, Leonardo Shu, Shijia Bian, Yang Sun, Ziyue Zeng"
date: "December 12, 2015"
output: html_document
---

The goal of our final project is a text mining for the twitter.

## List of Files for the Final Project 

`load_packages.R`


## Stage I: Load the Package

Before the anaysis, you need load the packages that are in the file `load_packages.R`.

```{r}
## Now we load the packages
EnsurePackage<-function(x)
{x <- as.character(x)
if (!require(x,character.only=TRUE))
{
  install.packages(pkgs=x,repos="http://cran.r-project.org")
  require(x,character.only=TRUE)
}
}

#Identifying packages required 
PrepareTwitter<-function()
{
  EnsurePackage("httr")
  EnsurePackage("devtools")
  EnsurePackage("twitteR")
  EnsurePackage("base64enc")
  EnsurePackage("stringr")
  EnsurePackage("ROAuth")
  EnsurePackage("RCurl")
  EnsurePackage("ggplot2")
  EnsurePackage("tm")
  EnsurePackage("RJSONIO")
  EnsurePackage("wordcloud")
  EnsurePackage("ggplot2") 
  EnsurePackage("streamR")
  EnsurePackage("NYU160J")
  EnsurePackage("grid")
}

PrepareTwitter()
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
